%% aesample.tex
%% Copyright 1999 Lars Engebretsen
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
% 
% The Current Maintainer of this work is Lars Engebretsen.
%
% This work consists of all files listed in MANIFEST.
%
\overfullrule=0pt
\def\TeX{T\kern-.12em\lower.37ex\hbox{E}\kern-.135emX}
\def\LaTeX{L\raise.42ex\hbox{\sc\kern-.5em A}\kern-.15em\TeX}
\def\iTeX{T\kern-.2em\lower.37ex\hbox{E}\kern-.08emX}
\def\iLaTeX{L\raise.5ex\hbox{\sc\kern-.45em A}\kern-.10em\iTeX}
\let\latex=\LaTeX
\def\fLaTeX{L\raise.42ex\hbox{\sc\kern-.39em A}\kern-.10em\TeX}
\def\sLaTeX{L\raise.42ex\hbox{\ssubfont\kern-.39em A}\kern-.10em\TeX}
\def\tex{\TeX}
\font\sc=cmr7 at 7pt
\font\bigE=cmmi10 at 14pt
\font\smallE=cmmi10 at 8pt
\def\E{~2\lower.08em\hbox{\Efont\char"F}}
\def\varE{~2\lower.08em\hbox{\Efont\char"22}}
\let\e=\varE
\let\Efont=\smallE
\def\it{\fam\itfam\font\sc=cmti7 at 7pt\let\tex=\iTeX\let\latex=\iLaTeX \tenit}
\def\bf{\fam\bffam\font\sc=cmbx7 at 7pt\tenbf}
%\def\bul{\leavevmode\llap{\vrule height.5em width.5em
%depth0pt\hskip.5em}} 
\def\bs{$\backslash$}
\def\vsm{\vskip2truept}


 \def\ams{{\the\textfont2 A}\kern-.1667em
 \lower.5ex\hbox{\the\textfont2 M}\kern-.125em
 {\the\textfont2 S}}
 \def\amstex{\ams-\TeX}

\font\Bsym=cmbsy10 at 28pt
\font\bbsym=cmbsy10 at 18pt
\def\amstexb{{\bbsym A}\kern-.1667em\lower.5ex\hbox
 {\bbsym M}\kern-.125em{\bbsym S}-\TeX}
\def\amsb{{\bbsym A}\kern-.1667em\lower.5ex\hbox
 {\bbsym M}\kern-.125em{\bbsym S}-\TeX}
\def\amsB{{\Bsym A}\kern-.1667em\lower.5ex\hbox
 {\Bsym M}\kern-.125em{\Bsym S}}

\font\bsym=cmbsy10 at 10.5pt
\def\amstexbh{{\bsym A}\kern-.1667em\lower.5ex\hbox
 {\bsym M}\kern-.125em{\bsym S}-\TeX}
\def\amsbh{{\bsym A}\kern-.1667em\lower.5ex\hbox
 {\bsym M}\kern-.125em{\bsym S}}

\def\pagenum{\ifnum\pageno=0\else\pagefont\folio\fi}
\headline={}
\footline{}

%\newdimen\pagemargin \pagemargin=.5in
\newdimen\pagemargin \pagemargin=.75in


\newdimen\pageheight \pageheight=11in
\advance\pageheight by -2\pagemargin

\newdimen\pagewidth \pagewidth=8.5in
\advance\pagewidth by -2\pagemargin

\newdimen\headcolumn \headcolumn=.334\pagewidth
\newdimen\bodycolumn \bodycolumn=.666\pagewidth

\vsize\pageheight % already includes top/bottom margin
%\advance\vsize by-\pagemargin

\def\raggedright{\rightskip 0pt plus 3em } % we'll be back
%\raggedbottom

\pretolerance=1000
\hyphenation{typeset typeset-ter typeset-ting Modern
Post-Script Textures Classic Hyper-Card pro-gram-mable}

\clubpenalty=10000
\widowpenalty=\clubpenalty
\hyphenpenalty=100
\doublehyphendemerits=10000000
\hsize=\pagewidth
\topskip 20pt
\leftskip=\headcolumn
\parskip=.2\baselineskip
\rightskip0pt plus .1\hsize
%\everypar{\looseness=-1 }
\setbox\strutbox=
 \hbox{\vrule height 9pt depth 4pt width0pt}


\emergencystretch .05\hsize


\vbadness10000 % Shut up

\font\chapterfont=cmssbx10 at 18pt
\font\headfont=cmssbx10 at 10.5pt
\font\subfont=cmss10 at 8pt
\font\ssubfont=cmss10 at 5.5pt
\font\pagefont=cmssbx10 at 9pt
\font\bignumfont=cmssbx10 at 15pt
\font\tt=cmtex10 at 10pt
\font\bodyfont=cmr10 at 10pt
\font\trade=cmr8 at 8pt
\fontdimen3\bodyfont=0.0pt
\font\tenit=cmti10 at 10pt
\font\tenbf=cmbx10 at 10pt
\fontdimen3\tenit=0.0pt
\fontdimen3\tenbf=0.0pt
\font\met=logo10 at 10pt
\font\tmfont=cmr17 at 4.5pt
\def\tm{\raise4pt\hbox{\tmfont TM}}
\font\mbsy=cmbsy10

\def\tagchar#1{\setbox0
  \hbox{\char#1}\ifdim\wd0>0pt\box0\hskip.3em\fi}
\def\tagfont#1#2{\hangafter=1\hang\noindent
  \font\tf=#1 at 10pt
  {\tf\count0=0\loop\tagchar{\count0}%
    \ifnum\count0<127\advance\count0by1\repeat}
  \par
}

\def\textsample#1#2#3
 {\raggedright
 {\font\ts=#1
 \ts\par
 \baselineskip= 1.2em
 #2\par
 #3\vskip 8pt}
 \rm
}

\def\chaptertype{\chapterfont\font\sc=cmssbx10 at 12pt
 \let\Efont=\bigE\let\e=\E
 \let\latex=\fLaTeX\baselineskip26pt\spaceskip0pt}
\def\headtype{\headfont\font\sc=cmssbx10 at 7pt
 \let\Efont=\smallE\let\e=\E
 \let\latex=\fLaTeX\baselineskip 13pt\spaceskip0pt}
\def\subtype{\subfont\baselineskip 11pt}
\def\bodytype{\bodyfont\baselineskip 13pt}
%\def\headpar{\rightskip\hsize minus\hsize\parindent0pt}
\def\headpar{\rightskip20pt plus3em minus1em\parindent0pt}
%\let\subpar=\headpar
\def\subpar{\rightskip25pt plus4em minus4em\parindent0pt}
\def\bodypar{\rightskip0pt plus4em\parindent0pt}

\bodytype
\parindent=0pt

\def\chapter#1#2\par{{\vfill\leftskip=0pt\hsize\pagewidth
 \null\vskip 22pt\chaptertype\headpar\noindent\uppercase{#1}\par
 \baselineskip13pt\null\hrule height 1pt\null
 \bodytype\bodypar\noindent\leftskip\headcolumn
 #2\par\null\vskip-2\baselineskip}}

\def\head#1#2\par{%
{\leftskip=0pt
 \setbox0=\vtop{\hsize\headcolumn\headtype\headpar\noindent#1\par}
 \dp0=0pt
 \null\null\hrule\null\nobreak
 \hbox{\box0\vtop{\hsize\bodycolumn\bodyfont\bodypar
 \noindent\ignorespaces#2\par}}\vskip4pt}} % the 4pt is a kludge - bs

\def\itemhead#1{%
{\leftskip=0pt
 \setbox0=\vtop{\hsize\headcolumn\headtype\headpar\noindent#1\par}
 \dp0=0pt
 \null\null\hrule\null\nobreak
 \hbox{\box0\vtop{\hsize\bodycolumn\bodyfont\bodypar
 }}\vskip-16pt}} % the 4pt is a kludge - bs

\def\sub#1#2\par{%
{\leftskip=0pt\setbox0=\vtop{\hsize\headcolumn\subtype\subpar\noindent#1\par}
 \dp0=0pt
 \vskip12pt\hrule height.2ptwidth\headcolumn\null\nobreak
 \hbox{\box0\vtop{\hsize\bodycolumn\bodyfont\bodypar
 \noindent\ignorespaces#2\par}}}}

\def\itemsub#1{%
{\leftskip=0pt\setbox0=\vtop{\hsize\headcolumn\subtype\subpar\noindent#1\par}
 \dp0=0pt
 \vskip12pt\hrule height.2ptwidth\headcolumn\null\nobreak
 \hbox{\box0\vtop{\hsize\bodycolumn\bodyfont\bodypar
 }}\vskip-\baselineskip}}

\def\emptychapter{\null\vskip-\parskip\vskip-2\baselineskip}
\def\emptyhead{\null\vskip-\parskip\vskip-2\baselineskip}

\def\bignumbox#1{\vbox to 0pt{\vss
 \hrule\hbox to 1.5\baselineskip{\vrule\hss\vbox to 1.5\baselineskip{
 \vss
 \bignumfont\hbox{#1}
 \vss
 }\hss\vrule}\hrule}}
\def\bignum#1{\vskip3.5\baselineskip\goodbreak\vskip-3.5\baselineskip
 \leavevmode\hangindent=2.\baselineskip\hangafter=-2\smash{%
 \hbox to 0pt{\hss\lower\baselineskip\bignumbox{#1}\hskip.5\baselineskip
 }}\ignorespaces}
\let\item=\bignum

\def\ms{\medskip}
\newcount\TestCount
\let\tex=\TeX
\def \LaTeX{\TestCount=\the\fam \leavevmode L\raise.42ex
\hbox{$\fam\TestCount\scriptstyle\kern-.3em A$}\kern-.15em\TeX}
\let\latex=\LaTeX
\def\LEX{L\lower.5ex\hbox{E}X}
\let\pcmf=\pcMF
\def\TUG{\TeX\ User Group}
\let\tug=\TUG
\font\eightss=cmss10 at 8pt
\font\sectiontitle=cmbx10 at 12pt
\font\sst=cmbx10
\font\bti=cmbxti10
\font\bt=cmb10
\font\fivsvtn=cmr5 at 17pt
\font\svtn=cmr17
\font\fiv=cmr5
\font\svtnfiv=cmr17 at 5pt

\newbox\leftbox
\def\makepage{\vtop{\hbox to\pagewidth{\the\headline}\box255}}
\newif\ifleft
\lefttrue
\output{\shipout\makepage\advancepageno}

\font\tiny=cmr17 at 4.25pt
\def\reg{\raise.4em\rlap{\trade ¨}}
\def\tm{\raise.4em\rlap{\tiny TM}}
\def\ltwoe{\LaTeX~$2\epsilon$}


\def\emptychapter{\null\vskip-\parskip\vskip-2\baselineskip}
\def\emptyhead{\null\vskip-\parskip\vskip-2\baselineskip}
\def\widedotfill{\leaders\hbox to 15pt{\hfil. \hfil}\hfill}
\def\page#1{\widedotfill#1\par}

\raggedright
\pretolerance=10000
\parindent=1.5em
\parskip=0.2\baselineskip
\font\capsmal=cmcsc10 at 5pt
\def\Textures{{\it Textures\/}}
\let\textures=\Textures
\def\tm{\raise.75ex\hbox{\capsmal TM}\kern-.0625em}
\font\tt=cmtt10
\font\eightit=cmti8
\font\title=cmr12 at 14pt
\font\cpsmcp=cmcsc10 scaled \magstep5
\font\subtitle=cmr12
\def\TeX{T\kern-.18em\lower.35ex\hbox{E}\kern-.09emX}
\let\tex=\TeX


%%%%%Preamble above!!!!!!!

{\parindent=0pt \obeylines \parskip=0pt \cpsmcp \baselineskip=1.05em
Computer
Modern
Faces
}

\eject

\headline={\hfill\pagenum}

\vskip -.3in

\chapter{Computer Modern PostScript Fonts}


\vskip .3in

{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt

The Computer Modern typefaces were created in the spirit of the typeface
Monotype Modern 8A by Professor Donald E. Knuth of Stanford University.  The
Computer Modern family includes a large set of scientific and mathematical
figures and symbols and is widely used with implementations of the \tex\
typesetting system.  {\it Computer Modern Typefaces}, Volume E of {\it
Computers and Typesetting} (D.~E.~Knuth, Addison Wesley), is the definitive
source for the Computer Modern faces. {\it The \tex book} (D.~E.~Knuth, Addison
Wesley), Appendix F, is also a good reference.

This package contains 75 faces from the Computer Modern family in Adobe
PostScript Type~1 form. These fonts can be used with all PostScript printers
and Adobe Type Manager.

}

\vskip -1in

\chapter{Font Samples, Text Faces}

\vskip .3in
\parindent 0pt

{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt

{\sst CM Bold}: cmb10
\vskip -2pt
\tagfont{cmb10}{}
\textsample{cmb10}{My beautiful new watch had run eighteen months
without losing or gaining, and without breaking any part of its
machinery or stopping. I had come to}

{\sst CM Bold Extended}: cmbx5, cmbx6, cmbx7, cmbx8, cmbx9, cmbx10, cmbx12
\vskip -2pt
\tagfont{cmbx10}{}
\bt cmbx5:
\vskip -2pt
\textsample{cmbx5}{believe it infallible in its judgments about the time of
day, and to consider its constitution and its anatomy imperishable. But at
last, one night, I let it run down. I grieved about it as if it were a}


\bt cmbx6:
\vskip -2pt
\textsample{cmbx6}{recognized messenger and forerunner of calamity. But by and
by I cheered up, set the watch by guess, and commanded my bodings and
superstitions to depart. Next day I stepped into}



\bt cmbx7:
\vskip -2pt
\textsample{cmbx7}{the chief jeweler's to set it by the exact time, and the
head of the establishment took it out of my hand and proceeded to set it for
me. Then he said, ``She is four}

}

\vfill\eject

{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt

\bt cmbx8:
\vskip -2pt
\textsample{cmbx8}{minutes slow---regulator wants pushing up.'' I tried to stop
him---tried to make him understand that the watch kept perfect time. But no;
all this human}


\bt cmbx9:
\vskip -2pt
\textsample{cmbx9}{cabbage could see was that the watch was four minutes slow,
and the regulator must be pushed up a little; and so, while I danced around him
in}


\bt cmbx10:
\vskip -2pt
\textsample{cmbx10}{anguish, and implored him to let the watch alone, he calmly
and cruelly did the shameful deed. My watch began to gain. It gained}


\bt cmbx12:
\vskip -2pt
\textsample{cmbx12}{faster and faster day by day. Within the week it sickened
to a raging fever, and its pulse went up to a hundred and fifty}


{\sst CM Bold Extended Slanted}: cmbxsl10
\vskip -2pt
\tagfont{cmbxsl10}{}
\textsample{cmbxsl10}{in the shade. At the end of two months it had left all
the timepieces of the town far in the rear, and was a fraction over thirteen
days}

{\sst CM Bold Extended Text Italic}: cmbxti10
\vskip -2pt
\tagfont{cmbxti10}{}
\textsample{cmbxti10}{ahead of the almanac. It was away into November enjoying
the snow, while the October leaves were still turning. It hurried}


{\sst CM Caps and Small Caps}: cmcsc10
\vskip -2pt
\tagfont{cmcsc10}{}
\textsample{cmcsc10}{up house rent, bills payable, and such things, in such a
ruinous way that I could not abide it. I took it to the watchmaker to be}


{\sst CM Dunhill}: cmdunh10
\vskip -2pt
\tagfont{cmdunh10}{}
\textsample{cmdunh10}{regulated. He asked me if I had ever had it repaired.  I
said no, it had never needed any repairing.  He looked a look of vicious
happiness and eagerly pried}

}

\eject


{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt
{\sst CM Funny Roman}: cmff10
\vskip -2pt
\tagfont{cmff10}{}
\textsample{cmff10}{the watch open, and then put a small dice-box into his eye
and peered into its machinery.  He said it wanted cleaning and oiling, besides
regulating---come in a week.  After being cleaned and}


{\sst CM Funny Italic}: cmfi10
\vskip -2pt
\tagfont{cmfi10}{}
\textsample{cmfi10}{oiled, and regulated, my watch slowed down to that degree
that it ticked like a tolling bell.  I began to be left by trains, I failed all
appointments, I got to}


{\sst CM Fibonacci}: cmfib8
\vskip -2pt
\tagfont{cmfib8}{}
\textsample{cmfib8}{missing my dinner; my watch strung out three days' grace to
four and let me go to protest; I gradually drifted back into yesterday, then
day}


{\sst CM Italic Typewriter}: cmitt10
\vskip -2pt
\tagfont{cmitt10}{}
\textsample{cmitt10}{before, then into last week, and by and by the
comprehension came upon me that all solitary and alone I was lingering along in
week before}


{\sst CM Roman}: cmr5, cmr6, cmr7, cmr8, cmr9, cmr10, cmr12, cmr17
\vskip -2pt
\tagfont{cmr10}{}
\bt cmr5:
\vskip -2pt
\textsample{cmr5}{last, and the world was out of sight. I seemed to detect in
myself a sort of sneaking fellow-feeling for the mummy in the museum, and a
desire to swap news with him. I went to a watchmaker again.  He took the watch}

\bt cmr6:
\vskip -2pt
\textsample{cmr6}{all to pieces while I waited, and then said the barrel was
``swelled.''  He said he could reduce it in three days.  After this the watch
averaged well, but nothing more.  For half a day it would go like}


\bt cmr7:
\vskip -2pt
\textsample{cmr7}{the very mischief, and keep up such a barking and wheezing
and whooping and sneezing and snorting, that I could not hear myself think for
the disturbance; and as long as it held out}


\bt cmr8:
\vskip -2pt
\textsample{cmr8}{there was not a watch in the land that stood any chance
against it.  But the rest of the day it would keep on slowing down and fooling
along until all the clocks it had left behind}

}

\eject

{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt

\bt cmr9:
\vskip -2pt
\textsample{cmr9}{caught up again.  So at last, at the end of twenty-four
hours, it would trot up to the judges' stand all right and just in time.  It
would show a fair and square average,}


\bt cmr10:
\vskip -2pt
\textsample{cmr10}{and no man could say it had done more or less than its
duty. But a correct average is only a mild virtue in a watch, and I took this
instrument to another}


\bt cmr12:
\vskip -2pt
\textsample{cmr12}{watchmaker.  He said the king-bolt was broken.  I said I was
glad it was nothing more serious.  To tell the plain truth, I had no idea}


\bt cmr17:
\vskip -2pt
\textsample{cmr17}{what the king-bolt was, but I did not choose to appear
ignorant to a stranger.  He repaired the king-}

{\sst CM Slanted}: cmsl8, cmsl9, cmsl10, cmsl12
\vskip -2pt
\tagfont{cmsl8}{}
\bt cmsl8:
\vskip -2pt
\textsample{cmsl8}{bolt, but what the watch gained in one way it lost in
another.  It would run awhile and then stop awhile, and then run awhile again,
and so on, using its own discretion about}

\bt cmsl9:
\vskip -2pt
\textsample{cmsl9}{the intervals.  And every time it went off it kicked back
like a musket. I padded my breast for a few days, but finally took the watch to
another watchmaker. He}

\bt cmsl10:
\vskip -2pt
\textsample{cmsl10}{picked it all to pieces, and turned the ruin over and over
under his glass; and then he said there appeared to be something the matter
with the hair-trigger.  He}

\bt cmsl12:
\vskip -2pt
\textsample{cmsl12}{fixed it, and gave it a fresh start.  It did well now,
except that always at ten minutes to ten the hands would shut together like a
pair of}

{\sst CM Slanted Typewriter}: cmsltt10
\vskip -2pt
\tagfont{cmsltt10}{}
\textsample{cmsltt10}{scissors, and from that time forth they would travel
together.  The oldest man in the world could not make head or tail of the time
of day}

{\sst CM Sans Serif}: cmss8, cmss9, cmss10, cmss12, cmss17
\vskip -2pt
\tagfont{cmss8}{}

}

\eject

{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt

\bt cmss8:
\vskip -2pt
\textsample{cmss8}{by such a watch, and so I went again to have the thing
repaired. This person said that the crystal had got bent, and that the
mainspring was not straight.  He also remarked that}


\bt cmss9:
\vskip -2pt
\textsample{cmss9}{parts of the works needed half-soling.  He made these things
all right, and then my timepiece performed unexceptionably, save that now and
then, after working}


\bt cmss10:
\vskip -2pt
\textsample{cmss10}{along quietly for nearly eight hours, everything inside
would let go all of a sudden and begin to buzz like a bee, and the hands would
straightway begin to spin}


\bt cmss12:
\vskip -2pt
\textsample{cmss12}{round and round so fast that their individuality was lost
completely, and they simply seemed a delicate spider's web over the face of the
watch.}


\bt cmss17:
\vskip -2pt
\textsample{cmss17}{She would reel off the next twenty-four hours in six or
seven minutes, and then stop with a bang.}


{\sst CM Sans Serif Bold Extended}: cmssbx10
\vskip -2pt
\tagfont{cmssbx10}{}
\textsample{cmssbx10}{I went with a heavy heart to one more watch\-maker, and
looked on while he took her to pieces.  Then I prepared to cross-question him
rigidly, for}


{\sst CM Sans Serif Demibold Condensed}: cmssdc10
\vskip -2pt
\tagfont{cmssdc10}{}
\textsample{cmssdc10}{this thing was getting serious.  The watch had cost two
hundred dollars originally, and I seemed to have paid out two or three thousand
for repairs.  While I waited and}

{\sst CM Sans Serif Italic}: cmssi8, cmssi9, cmssi10, cmssi12, cmssi17
\vskip -2pt
\tagfont{cmssi8}{}
\bt cmssi8:
\vskip -2pt
\textsample{cmssi8}{looked on I presently recognized in this watchmaker an old
acquaintance---a steamboat engineer of other days, and not a good engineer,
either.  He examined all the parts carefully,}


\bt cmssi9:
\vskip -2pt
\textsample{cmssi9}{just as the other watchmakers had done, and then delivered
his verdict with the same confidence of manner. He said: ``She makes too much
steam---you want to hang the}


\bt cmssi10:
\vskip -2pt
\textsample{cmssi10}{monkey-wrench on the safety-valve!'' I brained him on the
spot, and had him buried at my own expense. My uncle William (now deceased,
alas!) used to say that a}

}

\eject

{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt

\bt cmssi12:
\vskip -2pt
\textsample{cmssi12}{good horse was a good horse until it had run away once,
and that a good watch was a good watch until the repairers got a chance at it.
And}


\bt cmssi17:
\vskip -2pt
\textsample{cmssi17}{he used to wonder what became of all the unsuccessful
tinkers, and gunsmiths, and shoemakers, and}


{\sst CM Sans Serif Quotation Style}: cmssq8
\vskip -2pt
\tagfont{cmssq8}{}
\textsample{cmssq8}{engineers, and blacksmiths; but nobody could ever tell him.
\hskip 2em (Mark Twain, 1870)}


{\sst CM Sans Serif Quotation Italic Style}: cmssqi8
\vskip -2pt
\tagfont{cmssqi8}{}
\textsample{cmssqi8}{My beautiful new watch had run eighteen months without
losing or gaining, and without breaking any part of its machinery or
stopping. I had come to believe it}


{\sst CM Typewriter Caps and Small Caps}: cmtcsc10
\vskip -2pt
\tagfont{cmtcsc10}{}
\textsample{cmtcsc10}{infallible in its judgments about the time of day, and to
consider its constitution and its anatomy imperishable. But at last, one
night,}


{\sst CM Typewriter Extended}: cmtex8, cmtex9, cmtex10
\vskip -2pt
\tagfont{cmtex8}{}
\bt cmtex8:
\vskip -2pt
\textsample{cmtex8}{I let it run down. I grieved about it as if it were a
recognized messenger and forerunner of calamity. But by and by I cheered up,
set the watch by guess, and}


\bt cmtex9:
\vskip -2pt
\textsample{cmtex9}{commanded my bodings and superstitions to depart. Next day
I stepped into the chief jeweler's to set it by the exact time, and the head of
the}

\bt cmtex10:
\vskip -2pt
\textsample{cmtex10}{establishment took it out of my hand and proceeded to set
it for me. Then he said, ``She is four minutes slow---regulator wants}

}

\eject

{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt

{\sst CM Text Italic}: cmti7, cmti8, cmti9, cmti10, cmti12
\vskip -2pt
\tagfont{cmti7}{}
\bt cmti7:
\vskip -2pt
\textsample{cmti7}{pushing up.'' I tried to stop him---tried to make him
understand that the watch kept perfect time.  But no; all this human cabbage
could see was that the watch was four minutes}


\bt cmti8:
\vskip -2pt
\textsample{cmti8}{slow, and the regulator must be pushed up a little; and so,
while I danced around him in anguish, and implored him to let the watch alone,
he calmly and cruelly did the shameful}


\bt cmti9:
\vskip -2pt
\textsample{cmti9}{deed. My watch began to gain. It gained faster and faster
day by day. Within the week it sickened to a raging fever, and its pulse went
up to a hundred and fifty in the shade.}


\bt cmti10:
\vskip -2pt
\textsample{cmti10}{At the end of two months it had left all the timepieces of
the town far in the rear, and was a fraction over thirteen days ahead of the
almanac. It was away into}


\bt cmti12:
\vskip -2pt
\textsample{cmti12}{November enjoying the snow, while the October leaves were
still turning. It hurried up house rent, bills payable, and such things,}

{\sst CM Typewriter}: cmtt8, cmtt9, cmtt10, cmtt12
\vskip -2pt
\tagfont{cmtt8}{}
\bt cmtt8:
\vskip -2pt
\textsample{cmtt8}{in such a ruinous way that I could not abide it. I took it
to the watchmaker to be regulated.  He asked me if I had ever had it repaired.
I said no, it had never needed}


\bt cmtt9:
\vskip -2pt
\textsample{cmtt9}{any repairing.  He looked a look of vicious happiness and
eagerly pried the watch open, and then put a small dice-box into his eye and
peered into}


\bt cmtt10:
\vskip -2pt
\textsample{cmtt10}{its machinery.  He said it wanted cleaning and oiling,
besides regulating---come in a week.  After being cleaned and oiled, and
regulated,}


\bt cmtt12:
\vskip -2pt
\textsample{cmtt12}{my watch slowed down to that degree that it ticked like a
tolling bell.  I began to be left by trains, I failed all}


{\sst CM Unslanted Text Italic}: cmu10
\vskip -2pt
\tagfont{cmu10}{}

}

\eject

{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt

\textsample{cmu10}{appointments, I got to missing my dinner; my watch strung
out three days' grace to four and let me go to protest; I gradually drifted
back into}

{\sst CM Variable Typewriter}: cmvtt10
\vskip -2pt
\tagfont{cmvtt10}{}
\textsample{cmvtt10}{yesterday, then day before, then into last week, and by
and by the comprehension came upon me that all solitary and alone I was
lingering along in}

}

\vfill
\vskip -1.2in
\chapter{Font Samples, Symbols}

\vskip .2in
{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt
{\sst CM Bold Symbols}: cmbsy10
\vskip -2pt
\tagfont{cmbsy10}{}
\vskip 14pt

{\sst CM Inch}: cminch
\vskip -.65in
\textsample{cminch}{123ABC}

{\sst CM Math Extension}: cmex10
\vskip -2pt
\tagfont{cmex10}{}
\vskip 14pt

{\sst CM Math Italic}: cmmi5, cmmi6, cmmi7, cmmi8, cmmi9, cmmi10, cmmi12
\vskip -2pt
\tagfont{cmmi10}{}
\vskip 14pt

}

\vfill\eject

{\leftskip .3in\baselineskip1.2\baselineskip\hrule height0pt
{\sst CM Bold Extended Math Italic}: cmmib10
\vskip -2pt
\tagfont{cmmib10}{}
\vskip 14pt

{\sst CM Symbols}: cmsy5, cmsy6, cmsy7, cmsy8, cmsy9, cmsy10
\vskip -2pt
\tagfont{cmsy8}{}

}

\eject

\end
