\documentclass{article}
\usepackage[german]{babel}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{times}

\begin{document}

In addition, this theory---that of the German sociologist Niklas
Luhmann---is one 
of the most (if not the most) powerful
contemporary general sociological theories
\citep{luhm:DoS,Luhm:Soc&int,luhm:WrtdG}.  Therefore, in the rest of
this section, rather than making an eclectic use of different social
theories, I briefly present portions of Luhmann's theory.

\begin{thebibliography}{3}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[Luhmann(1982)]{luhm:DoS}
Niklas Luhmann.
\newblock {\em The Differentiation of Society}.
\newblock New York: Columbia University Press, 1982.

\bibitem[Luhmann(1987)]{Luhm:Soc&int}
Niklas Luhmann.
\newblock The evolutionary differentiation between society and interaction.
\newblock In Jeffrey~C. Alexander, Bernhard Giesen, Richard Muench, and Neil~J.
  Smelser, editors, {\em The Micro-Macro Link}, pages 112--31. Berkeley:
  University of California Press, 1987.

\bibitem[Luhmann(1988)]{luhm:WrtdG}
Niklas Luhmann.
\newblock {\em Die Wirtschaft der Gesellschaft}.
\newblock Frankfurt am Main: Suhrkamp, 1988.

\end{thebibliography}
\end{document}
\usepackage
[%linkcolor=yellow,
 citecolor=yellow,
 citebordercolor={.5 .5 0},
 pdftitle={Testing natbib and hyperref},
 pdfauthor={SPQR and PWD},
 pdfsubject={Dummy stuff},
 pdfkeywords=Luhmann,
% pdfstartview=/FitB,
 pdfpagemode=UseThumbs 
]
{hyperref}
